% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2010 Jason R. Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[english]{isodate}\isodate
\usepackage{fullpage,url}

% Fonts
\usepackage[T1]{fontenc}
%\usepackage[urw-garamond]{mathdesign}

% Set your name here
\def\name{Jed Brown}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {glaciology, computational science, partial differential equations, finite element methods, incompressible flow, non-Newtonian flow, boundary conditions},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

% \geometry{
%   body={6.5in, 9.0in},
%   left=1.0in,
%   top=1.0in
% }

% % Customize page headers
% \pagestyle{myheadings}
% \markright{\name}
% \thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

\newcommand\ptitle[1]{\textit{#1}} % Formatting for paper titles

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
    \setlength{\itemsep}{0.25em}
    \setlength{\parskip}{0pt}
    \setlength{\parsep}{0.25em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\LARGE \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\bigskip

\begin{minipage}[t]{0.5\textwidth}
  \begin{tabular}{l}
  Mathematics and Computer Science Division \\
  Argonne National Laboratory \\
  9700 S Cass Ave \\
  Argonne, IL 60439, USA
\end{tabular}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  \begin{tabular}{ll}
    % Office: +41 44 632 4147 \\
    Mobile: & +1 773 234 5332 \\
    Fax: & +1 630 252 5986 \\
    Email: & \url{jedbrown@mcs.anl.gov}
  \end{tabular}
\end{minipage}

\section*{Education}

\begin{itemize}
\item Ph.D. Glaciology, ETH Z\"urich, 2011.
\item M.S. Mathematics, University of Alaska Fairbanks, 2006.
\item B.S. Mathematics, {\it magna cum laude}, University of Alaska Fairbanks, 2004.
\item B.S. Physics, {\it magna cum laude}, University of Alaska Fairbanks, 2004.
\end{itemize}

\section*{Employment}
\begin{itemize}
\item Postdoctoral Fellow, Mathematics and Computer Science Division, Argonne National Laboratory, 2011--present
\item Research Assistant, ETH Z\"urich, 2007--2011
\item Research Technician, University of Alaska Fairbanks, 2006--2007
\item Research Assistant, University of Alaska Fairbanks, 2003--2006
%\item Teaching Assistant, University of Northern British Columbia, 2003
%\item Student Assistant, Geophysical Institute, 2002
\end{itemize}

\section*{Research}
\begin{itemize}\item Scalable solvers for implicit multiphysics, high order PDE
  discretization in complex geometry, compatible discretizations for
  heterogeneous flows, PDE-constrained optimization.
\end{itemize}
\subsection*{Selected publications}
\begin{itemize}
\item R.J. Biezuner, J. Brown, G. Ercole, and E. M. Martins, \ptitle{Computing the first eigenpair of the $p$-Laplacian via inverse iteration of sublinear supersolutions}, accepted by J. Scientific Computing, 2011.
\item J. Brown, B. Smith, and A. Ahmadia, \ptitle{Achieving textbook multigrid efficiency for hydrostatic ice sheet flow}, submitted to SIAM J. Sci. Comput., 2011.
\item J. Brown, \ptitle{Efficient nonlinear solvers for nodal high-order finite elements in 3D}, Journal of Scientific Computing, 45(1) 48--63, 2010.
\item J. M. Amundson, M. Fahnestock, M. Truffer, J. Brown, M. P. L\"uthi, and R. J. Motyka, \ptitle{Ice m\'elange dynamics and implications for terminus stability, Jakobshavn Isbr\ae, Greenland}, Journal of Geophysical Research, Earth Surface, 115, F01005, 2010.
\item K. Burckhardt, D. Szczerba, J. Brown and K. Muralidhar, and G. Szkely. \ptitle{Fast implicit simulation of oscillatory flow in human abdominal bifurcation using a Schur complement preconditioner}, Euro-Par Parallel Processing, 747-759, 2009.
\item E. Bueler and J. Brown, \ptitle{The shallow shelf approximation as a `sliding law' in a thermomechanically coupled ice sheet model}, Journal of Geophysical Research, Earth Surface. 114, F03008, 2009.
\item E. Bueler, J. Brown, and C. Lingle, \ptitle{Exact solutions to the thermocoupled shallow ice approximation: effective tools for verification}, Journal of Glaciology. 53(182), 499-516, 2007.
\item E. Bueler, C. S. Lingle, J. Brown. \ptitle{Fast computation of a viscoelastic deformable earth model for ice flow simulations}, Annals of Glaciology. 46, 97-106, 2007.
\item E. Bueler, C. S. Lingle, J. A. Kallen-Brown, D. N. Covey, and L. N. Bowman, \ptitle{Exact solutions and the verification of numerical models for isothermal ice sheets}, Journal of Glaciology, 51(173), 2005.
\end{itemize}

\subsection*{Selected conference presentations}
\begin{itemize}
\item Jed Brown, Dave May, and Barry Smith, \ptitle{Strongly coupled solvers with loosely coupled software}, 7th International Congress on Industrial and Applied Mathematics - ICIAM 2011, Vancouver, Canada, 2011-07-21.
\item Jed Brown, Iulian Grindeanu, Dmitry Karpeev, Barry F. Smith, and Timothy J. Tautges, \ptitle{Scalable implicit methods for free surface flows in glaciology}, 7th International Congress on Industrial and Applied Mathematics - ICIAM, Vancouver, Canada, 2011-07-20.
\item J. Brown, \ptitle{Implicit solution of free surface flows in glaciology}, SIAM Conference on Computational Science and Engineering, Reno, NV, \printdate{2011-03-01}.
\item J. Brown, \ptitle{Computational methods for several models of ice stream flow}, International Conferenece on the Diversity of Research on Geophysical Environmental Sciences, ETH Z\"urich, \printdate{2011-02-18}.
\item J. Brown, \ptitle{Solving free surface flows for steady state without time stepping}, American Geophysical University Fall Meeting, \printdate{2010-12-14}.
\item J. Brown, \ptitle{Implicit discretizations for grounding line dynamics}, CCSM Annual Meeting, Breckenridge, CO,  \printdate{2010-06-30}.
\item J. Brown, \ptitle{PETSc: new developments, memory performance, and algorithmic experimentation}, NOTUR, Bergen, Norway, \printdate{2010-05-21}.
\item J. Brown, \ptitle{Implicit integration of 3D ice sheet flow using hybrid factorization/relaxation block preconditioning}, invited, Copper Mountain Conference on Iterative Methods, CO, \printdate{2010-04-08}.
%\item J. Brown and B. Smith, \ptitle{Textbook multigrid efficiency for hydrostatic ice flow}, CCSM Land Ice Working Group, Boulder, CO, \printdate{2010-02-17}.
%\item J. Brown, \ptitle{Accurate Time Integration of 3D Grounding Line Dynamics}, American Geophysical Union Fall Meeting, \printdate{2009-12-15}.
%\item J. Brown, \ptitle{Scalable solvers for the 3D non-Newtonian Stokes problem in ice flow modeling}, CCSM Annual Meeting, Breckenridge, CO, \printdate{2010-06-17}.
%\item J. Brown, \ptitle{Scalable solvers for optimal control of a power-law fluid}, American Geophysical Union, Fall Meeting \printdate{2008-12-15}.
\end{itemize}

\subsection*{Software}
\begin{itemize}
\item Principal author of the Parallel Ice Sheet Model (PISM) 2004--2007, \url{http://pism-docs.org}.
\item Developer of the PETSc solvers package since 2008, \url{http://mcs.anl.gov/petsc}.
\item Author of the Dohp finite element library, \url{https://github.com/jedbrown/dohp}.
\end{itemize}

% \subsection*{Funding}
% \begin{itemize}
% \item The causes and future direction of the rapid thinning and acceleration of Jakobshavn Isbr{\ae}, West Greenland Swiss National Science Foundation, 2007-2010
% \item Scalable Ice-sheet Solvers and Infrastructure for Petascale, High-resolution, Unstructured Simulations, DOE ASCR LAB 09-21, 2009-2012
% \end{itemize}

% \subsection*{Collaborators}
% \begin{itemize}
% \item Ed Bueler, Martin Truffer, (University of Alaska);
%   Jason Amundson (University of Chicago); Mark Fahnestock (University of New
%   Hampshire); Martin Funk, Wolfgang Kinzelbach, Martin L\"uthi, Dave May
%   (ETH, Swiss Federal Institute of Technology Z\"urich); Dmitry Karpeev,
%   Barry Smith, Tim Tautges, Jean Utke (Argonne National Laboratory);
%   Patrick Heimbach (Massachusetts Institute of Technology)
% \end{itemize}
\section*{Other}
\subsection*{Tutorials}
\begin{itemize}
\item J. Brown, \ptitle{PETSc} tutorial at the 2011 ACTS workshop, NERSC, Berkeley, CA, \printdate{2011-08-17}.
\item J. Brown, \ptitle{PETSc}, 3-day tutorial at the Arctic Region Supercomputing Center, Fairbanks, AK, \daterange{2010-08-03}{2010-08-05}.
\item J. Brown, \ptitle{PETSc}, 2-day tutorial at the Swiss National Supercomputing Center, Manno, Switzerland, \daterange{2010-05-10}{2010-05-11}.
\item J. Brown, \ptitle{Scalable solvers for nonlinear equations: mini-course on Newton-Krylov methods}, 3-week mini-course at the University of Alaska Fairbanks, \daterange{2009-01-22}{2009-02-05}, \href{http://59A2.org/newton-krylov/}{\url{59A2.org/newton-krylov}}.
\end{itemize}

% \subsection*{Honors \& Awards}
% \begin{itemize}
% \item 2004 Outstanding Mathematics Student of the Year, UAF
% \item 2004 Outstanding Physics Student of the Year, UAF
% \item 2000--2004 Alaska Scholar
% \end{itemize}

% Footer
\begin{center}
  \begin{small}
    Last updated: \today
  \end{small}
\end{center}
\end{document}
